On Secure Delegation of SampBQP with a Classical Client

### 2019-11-24 qpip.tex
Type out permutation invariance argument

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{Our $\QPIP_{XZ}$ protocol}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\State Pick $n$ large enough so, $P\left[Bin(n, \frac{1}{2}-\varepsilon)<\left(\frac{1}{2}-2\varepsilon\right)n\right]$ is negligible in $\varepsilon$ by Chernoff bound
		\State Pick $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}=O(\poly(\varepsilon))$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
		\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\State The verifier randomly picks $n+m$ copies in sequence and without replacement
		\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
		\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
			\For{$i\gets 1, m$}
				\State Measure the time register of a (supposedly) fresh copy of $\ket{\psi_{C(x)}}$ that the prover sent
				\If{Measured $t\geq T$}
					\State Measure and output the other registers
				\EndIf
			\EndFor
			\State Reject
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}

We first apply \autoref{deFinetti}. This is justified because... TODO

So, with some error $O(\poly(\varepsilon))$ in measurement results, we can assume without the loss of generality that the rest of the algorithm acts on an input of the form... TODO.

Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.

Let $q_j$ be the accept probability of $\ket{\rho_j^{\otimes n+m}}$ under \autoref{AlgAmp1}. By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_j^{\otimes n+m}}$ is then $\frac{w_j q_j}{\sum_i w_i q_i}$.

>>>>

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{Our $\QPIP_{XZ}$ protocol}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\State Pick $n$ large enough so, $P\left[Bin(n, \frac{1}{2}-\varepsilon)<\left(\frac{1}{2}-2\varepsilon\right)n\right]$ is negligible in $\varepsilon$ by Chernoff bound
		\State Pick $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}=O(\poly(\varepsilon))$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
		\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\State The verifier randomly picks $n+m$ copies in sequence and without replacement
		\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
		\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
			\For{$i\gets 1, m$}
				\State Measure the time register of a fresh copy from the prover
				\If{Measured $t\geq T$}
					\State Measure and output the other registers
				\EndIf
			\EndFor
			\State Reject
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}

This clearly has completeness negligibly close to $1$. Now we analyze soundness, for a possibly cheating prover.

Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state at that point as

$$\sigma'=\frac{1}{\abs{\Sym(N)}}\sum_{\Pi\in\Sym(N)}\Pi\sigma\Pi^\dagger$$

Let $\tilde{\Pi}$ be some fixed permutation. Then it is easy to check that

$$\tilde{\Pi}\sigma'\tilde{\Pi}^\dagger=\sigma'$$

So $\sigma'$ is permutation-invariant and we can apply \autoref{deFinetti}:

$$\norm{\sigma'-\sum_i w_i\rho_i^{\otimes n+m}}=O(\poly(\varepsilon))$$

Note that this is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.

Let $q_j$ be the accept probability of $\ket{\rho_j^{\otimes n+m}}$ under \hyperref[AlgAmp1]{Protocol~\ref*{AlgAmp1}}. By Bayes' theorem, conditioned on acceptance, the probability of the input being $\ket{\rho_j^{\otimes n+m}}$ is then $\frac{w_j q_j}{\sum_i w_i q_i}$.
